SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-28 2017-Xudong-SMT/ActaInformatica.tex
Refine the proof of Th.2 after the discussion with Prof.Min.

Suppose that  $\ostate{\tilde{t}}\in States(L1_{reach})$, it is reachable in the result automaton of Algorithm 1, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t}}$ where $Pred_i$ are all satisfiable. And there exists $\ostate{\tilde{u}}\in States(L2_{reach})$ where $\ostate{\tilde{t}}=\ostate{\tilde{u}}$.

Similarly, from the structure of the algorithms, 
\[\forall \ostate{\tilde{u}}\in States(L2_{reach}), \exists\ostate{\tilde{t}}\in States(L1), \ostate{\tilde{t}}=\ostate{\tilde{u}}\]
\[s.t.\quad OT_t = \ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}\in L1, OT_u = \ostate{\tilde{u}}\xrightarrow{v}\ostate{\tilde{u'}}\in L2_{reach}, Rename(OT_t) = OT_u.\]
where $Pred_t$ and $Pred_u$ are satisfiable.

Then we can get a new longer sequence $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t'}}$ implying that $\ostate{\tilde{t'}}\in States(L1_{reach}),OT_t\in L1_{reach}$. So 
$States(L2_{reach})\subseteq  States(L1_{reach})$.

Moreover,
\[\forall OT_u\notin L2_{reach}, \exists OT_t\in L1, Rename(OT_t) = OT_u\]
where $Pred_t$ and $Pred_u$ are not satisfiable. Then according to the pruning function in Algorithm 1, $OT_t\notin L1_{reach}$.

>>>>

If there is an initial state $\ostate{\tilde{t_0}}\in States(L2_{reach})$ then the initial state of the original automaton $\ostate{\tilde{t_0}}\in States(L1_{reach})$ must exists.

Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$, it is reachable in the result automaton of Algorithm 2, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where $Pred_j$ are all satisfiable. Then there exists the same state $\ostate{\tilde{t}}\in States(L1_{reach})$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t}}$ where $Pred_i$ are all satisfiable.
From the structure of the algorithms, 
\[\forall \ostate{\tilde{t}}\in States(L2_{reach}), OT = \ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}\in L2_{reach}\]
\[\exists OT' = \ostate{\tilde{t}}\xrightarrow{v'}\ostate{\tilde{t'}}\in L1 \quad s.t.\quad Rename(OT') = OT.\]
where $Pred$ and $Pred'$ are satisfiable.

Then we can get a new longer sequence $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t'}}\xrightarrow{v'}\ostate{\tilde{t'}}$ implying that $\ostate{\tilde{t'}}\in States(L1_{reach}),OT'\in L1_{reach}$. So 
$L2_{reach}\subseteq  L1_{reach}$.

Moreover,
\[\forall OT\notin L2_{reach}, \exists OT'\in L1, Rename(OT') = OT\]
where $Pred$ and $Pred'$ are not satisfiable. Then according to the pruning function in Algorithm 1, $OT'\notin L1_{reach}$.
